% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{COMP230 - Ethics and Professionalism - Are loot boxes a type of gambling?}

% Please put your student number in the author field
\author{1507729}

\begin{document}

\maketitle

\section{Proposal}
According to the Oxford Dictionary one of uses for the verb Gambling is as follows "Take risky action in the hope of a desired result."

The games industry is filled with microtransactions in all kinds of forms, these are designed to enhance the gameplay experience of the player by adding or unlocking content. In recent years however microtransactions have started to adapt a loot box system which allows players to pay a small amount to unlock boxes with a chance to obtain various in-game items or cosmetics that the player wants or needs.

Many of these microtransactions however are being tailored to maximise the amount that people will spend during their time playing the game. They are using many of the same tactics used within the gambling industry to capitalise on people who have addictive tendencies. With many of the games who use this model designing their game around creating a need for these types of transaction, but not letting players purchase exactly what they want. With the option of spending many hours in game or to pay real world money to possibly unlock the content the player wants or needs to progress. The question is does this count as gambling and should it be enforced?


\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}
